MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident angle

### 2022-01-25 paper.tex
updates

\begin{figure}[!hbt]
\includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
\caption{ \textcolor{red}{plots should be updated} Schematic view of the sampling calorimeter. It consists of 105 alternating lead plates and scintillator strips. Each scintillator layer consists of 35 scintillator strips. The cross section of each 1-mm-thick lead plate is 525 mm $\times$ 525 mm. The cross section of each 5-mm-tihck scintillator strip is 525 mm $\times$ 15 mm. }
\label{fig:det_conf}
\end{figure}

@@

\begin{figure}[!hbt]
\includegraphics[width=0.89\textwidth]{figures/optimization_plot.pdf}
\caption{The angular resolution for the varying N\_estimators and the varying Max. depth. The best angular resolution is obtained with N\_estimators=300 and Max. depth=100.  }
\label{fig:par_scan}
\end{figure}

>>>>

\begin{figure}[!hbt]
\includegraphics[width=0.6\textwidth]{figures/FullLayer_2.jpeg}
\caption{ Schematic view of the sampling calorimeter. It consists of 105 alternating lead plates and scintillator strips. Each scintillator layer consists of 35 scintillator strips. The cross section of each 1-mm-thick lead plate is 525 mm $\times$ 525 mm. The cross section of each 5-mm-tihck scintillator strip is 525 mm $\times$ 15 mm. }
\label{fig:det_conf}
\end{figure}

@@

\begin{figure}[!hbt]
\includegraphics[width=0.89\textwidth]{figures/optimization_plot.pdf}
\caption{The angular resolution for the varying N\_estimators and the varying Max. depth. The best angular resolution is obtained with N\_estimators~=~300 and Max. depth~=~100. }
\label{fig:par_scan}
\end{figure}
